TBD

### 2021-03-15 outputs/paper/paper.Rmd
formula update

```{r setup, include=FALSE,echo=FALSE, warning=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(hrbrthemes)
library(kableExtra)
library(broom)

@@

@@

In the statistical analysis aspect, unpaired two-sample t-tests were applied to test whether deepfake videos are statistically different from other media formats at the deception level. The results from Table \@ref(tab:ttest1) to Table \@ref(tab:ttest3) show that only the difference in the deception level between video and skit is significant(p<0.01). The p-values for comparing video and text, video and audio are larger than 0.05, which means there is not sufficient evidence to support video is different from the audio or text. In other words, videos do not differ from audio or text significantly.

@@

### Affect Level
The unpaired two-sample t-tests were utilized to investigate whether there is a different emotional impact on the target elite between deepfake videos and other conditions, including different deepfake formats and control groups that no clip at all.

The result of comparing the deepfake video and the control group in Table \@ref(tab:attest1) demonstrates that the video condition will cause a negative sentimental effect from people to Elizabeth Warren. The 95% confidence interval shows that the true difference in means is between -1.35 and -7.72. Given the p-value less than 0.05, the difference between the two groups is significant.

@@

Similarly, the same analysis has been done for the rest unpaired two-sample t-tests. In our study, we used 5% significance level. Table \@ref(tab:attest2) shows the test result of how deepfake videos and texts impact audiences feeling. The result shows that the difference in affect level between video (Mean = 41.28) and text (Mean=44.22) was not significant given the p-value is greater than 0.05.

@@

Table \@ref(tab:attest3) shows the test result of how deepfake videos and audios impact audiences feeling. The difference in affect level between video(Mean = 41.28) and audio (Mean=43.93) was not significant given the p-value is greater than 0.05.
```{r attest3, echo=FALSE, fig.width=10, fig.height=3}
#video vs audio
t3_a<-t.test(na.omit(dat$post_favor_Warren[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Warren[dat$treat_fake_audio == 1]))

@@

### Model Results
Multiple linear regression was applied to use the top 20 important explanatory variables generated from the random forests model to predict the affect level.

As shown in the summary table, only 9 variables are significant (p<0.05) to the affect level to Elizabeth Warren which are education level is postgraduate; income in the range of \$100k to $150k; live in the Northeast in the US; whether age larger than 65; partisan; ambivalent sexism; and treat is advertisement.

@@

@@

model <- lm(post_favor_Warren ~., data =FS )
```

```{r regression, echo=FALSE, warning=FALSE, fig.width=10, fig.height=4,message=FALSE}
## stargazer package to show table results
#install.packages("array")
library(stargazer)

@@

In addition, in the Scale-Location plot (Figure \@ref(fig:figure1) in Appendix), an approximate horizontal line being shown, which means the residuals are randomly distributed and have constant variance. The Normal QQ-plot (Figure \@ref(fig:figure2) in Appendix) shows almost all the residuals match the diagonal line. The Residual versus Leverage plot(Figure \@ref(fig:figure3) in Appendix) shows that there is no evident of outliers, and none of the points come close to having both high residual and leverage.

>>>>

```{r setup, include=FALSE,echo=FALSE, warning=FALSE, message=FALSE}
chooseCRANmirror(graphics=FALSE, ind=1)
knitr::opts_chunk$set(echo = TRUE)

library(tinytex)
library(tidyverse)
library(palmerpenguins)
library(ggplot2)
library(ggthemes)
library(ggpubr)
library(hrbrthemes)
library(kableExtra)
library(broom)

@@

# Model

$$
\hat Y =\hat \beta_0+\hat \beta_1I_{gender:male}+\hat \beta_2I_{gender:other}+\hat \beta_3I_{High school} +\hat \beta_4I_{College}+\hat \beta_5I_{Postgraduate}+\hat \beta_6I_{HHI100K-150k}+\hat \beta_7I_{HHI>150K}$$
$$+\hat \beta_8I_{HHI25K-49K}+\hat \beta_9I_{HHI50K-74K}+\hat \beta_{10}I_{HHI75K-99K}+\hat \beta_{11}I_{HHIN/A}+\hat \beta_{12}I_{Ethnicity:Black}+\hat \beta_{13}I_{Ethnicity:other}$$
$$+\hat \beta_{14}I_{Ethnicity:white}+\hat \beta_{15}I_{Region:Northeast}+\hat \beta_{16}I_{Region:South}+\hat \beta_{17}I_{Region: West}+\hat \beta_{18}I_{WaveID:SVeyxdeXOuISXzakt}$$
$$+\hat \beta_{19}I_{Meta:OSmobile}+\hat \beta_{20}I_{Age>65}+\hat \beta_{21}I_{PID:Independent}+\hat \beta_{22}I_{PID:Republican}+\hat \beta_{23}*{AmbivalentSexism}+\hat \beta_{24}*{PLK}$$
$$+\hat \beta_{25}I_{Video}+\hat \beta_{26}I_{audio}+\hat \beta_{27}I_{Text}+\hat \beta_{28}I_{Skit}+\hat \beta_{29}I_{Ad}+\hat \beta_{30}I_{Script:bidenshit}+\hat \beta_{31}I_{Script:trumpshit}+\hat \beta_{32}I_{Script:cherokee}$$
$$+\hat \beta_{33}I_{Script:lgbtq}+\hat \beta_{34}I_{Info}+\hat \beta_{35}*{PDL}+\hat \beta_{36}*{InternetUsage}+\hat \beta_{37}*{CRT}+\epsilon$$

@@

In the statistical analysis aspect, unpaired two-sample t-tests were applied to test whether deepfake videos are statistically different from other media formats at the deception level. The results from Table \@ref(tab:ttest1) to Table \@ref(tab:ttest3) show that only the difference in the deception level between video and skit is significant (p<0.01). The p-values for comparing video and text, video and audio are larger than 0.05, which means there is not sufficient evidence to support that video is different from the audio or text. In other words, videos do not differ from audio or text significantly.

@@

### Affect Level
The unpaired two-sample t-tests were utilized to investigate whether there is a different emotional impact on the target elite between deepfake videos and other conditions, including different deepfake formats and control groups that have no clip at all.

The result of comparing the deepfake video and the control group in Table \@ref(tab:attest1) demonstrates that the video condition will cause a negative sentimental effect from respondents to Elizabeth Warren. The 95% confidence interval shows that the true difference in means is between -1.35 and -7.72. Given the p-value less than 0.05, the difference between the two groups is significant.

@@

Similarly, the same analysis has been done for the rest unpaired two-sample t-tests. In our study, we used a 5% significance level. Table \@ref(tab:attest2) shows the test result of how deepfake videos and texts impact audiences' feelings. The result shows that the difference in affect level between video (Mean = 41.28) and text (Mean=44.22) was not significant given the p-value is greater than 0.05.

@@

Table \@ref(tab:attest3) shows the test result of how deepfake videos and audios impact audiences' feelings. The difference in affect level between video(Mean = 41.28) and audio (Mean=43.93) was not significant given the p-value is greater than 0.05.
```{r attest3, echo=FALSE, fig.width=10, fig.height=3}
#video vs audio
t3_a<-t.test(na.omit(dat$post_favor_Warren[dat$treat_fake_video == 1]), 
       na.omit(dat$post_favor_Warren[dat$treat_fake_audio == 1]))

@@

### Model Results
Multiple linear regression was applied to use the top 20 important explanatory variables generated from the random forest model to predict the affect level.

As shown in the summary table, only 9 variables are significant (p<0.05) to the affect level to Elizabeth Warren which are postgraduate education level is; income ranging in $100k to $150k; living in the Northeast of  US; whether age older  than 65; partisan; ambivalent sexism; and treat is advertisement.

@@

model <- lm(post_favor_Warren ~., data =FS )

## stargazer package to show table results
#install.packages("array")

library(stargazer)

@@

@@

In addition, in the Scale-Location plot (Figure \@ref(fig:figure1) in Appendix), an approximately horizontal line is shown, which means the residuals are randomly distributed and have constant variance. The Normal QQ-plot (Figure \@ref(fig:figure2) in Appendix) shows almost all the residuals match the diagonal line, meaning the residuals are normally distributed. The Residual versus Leverage plot (Figure \@ref(fig:figure3) in Appendix) shows that there is no evidence of outliers, and none of the points come close to having both high residual and leverage.
